Chemical tagging can work: \\ Identification of stellar phase-space structures \\ purely by chemical-abundance similarity

### 2016-01-18 papers/clusters.tex
I definitely think that this is something that we would forget to remove later on. Therefore, I'm saving my collective ass by removing it now. Sorry @davidwhogg

Our specific contribution in this space has been to develop
\thecannon\ \citep{thecannon, ages}, which is a data-driven model for
stellar spectra.
This model can deliver stellar parameters and chemical abundances for
stars, making use of every pixel of every stellar spectrum (that is,
all the information in the data) but making no use at all of physical
models of stars.
It relies only on there being training data---\emph{some} stars for
which parameters and abundances are known and believed.
In companion papers \citep{casey16, ness16} we show that
\thecannon\ can deliver 15 to 19 abundances for stars in the
\apogee\ survey, at precisions higher than even the training data on
which the model is trained.
We say more about this below.
We will show here that \thecannon\ improves chemical abundance measurements
to the point that \emph{chemical tagging is now possible.}
We have thereby effectively saved the collective asses of all the
collaborators in all of the above-referenced large spectroscopic
surveys.

>>>>

Our specific contribution in this space has been to develop
\thecannon\ \citep{thecannon, ages}, which is a data-driven model for
stellar spectra.
This model can deliver stellar parameters and chemical abundances for
stars, making use of every pixel of every stellar spectrum (that is,
all the information in the data) but making no use at all of physical
models of stars.
It relies only on there being training data---\emph{some} stars for
which parameters and abundances are known and believed.
In companion papers \citep{casey16, ness16} we show that
\thecannon\ can deliver 15 to 19 abundances for stars in the
\apogee\ survey, at precisions higher than even the training data on
which the model is trained.
We say more about this below.
We will show here that \thecannon\ improves chemical abundance measurements
to the point that \emph{chemical tagging is now possible.}
